Refinements for open pNets

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
petit ajout

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update. Our definition captures a simple kind of sub-classing of open automata with the same holes. It is stronger than a strict simulation since it matches a transition with a family of transitions. With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc...

>>>>

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update. Our definition captures a simple kind of sub-classing of open automata with the same holes. It is stronger than a strict simulation since it matches a transition with a family of transitions. With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables. However, this refinement is inappropriate is the setting of composability which is the main advantage of the pNets-based approach. Refinement through composition  leads to a model, in which composition can be used both to add new holes to a system and to restrict the holes already present to a subset.
